---
title: "Assignment 4"
author: "Kyle Walker"
date: "9/24/2019"
output: 
        #pdf_document: default
        rmarkdown:: github_document
---

#### 1. Compute the follows using %>% operator. Notice that
##### • x %>%\ f = f(x),
##### • x %>% f %>% g = g(f(x)) and
##### • x %>% f(y) = f(x,y)
##### a. sin(2019)
```{r}
library(dplyr)
2019 %>% 
  sin()
```

##### b. sin(cos(2019))
```{r}
2019 %>% 
  cos() %>% 
    sin()
```

##### c. sin(cos(tan(log(2019))))
```{r}
2019 %>% 
  log() %>% 
    tan() %>% 
      cos() %>% 
        sin()
```

##### d. log2(2019)
```{r}
2019 %>% 
  log2()
```

#### 2. Fixing the SEX, AGE and TRAV_SP following the steps in Assignment 2 (This time, do it on the entire dataset instead of the sample dataset).
```{r}
library(readxl)
library(stringr)
c2015 <- read_excel("C:/Users/student/Documents/Senior Year/MATH 421/Assignment 2/c2015.xlsx")
#Fixing Sex
c2015$SEX[is.na(c2015$SEX)]<- "Female"
#Fixing Age
c2015$AGE[c2015$AGE == 'Less than 1'] <- "0"
c2015$AGE <- as.numeric(c2015$AGE)
c2015$AGE[is.na(c2015$AGE)] <- mean(c2015$AGE)
#Fixing Trav_Sp
c2015$TRAV_SP <- str_replace(c2015$TRAV_SP, " MPH", "")
c2015$TRAV_SP <- str_replace(c2015$TRAV_SP, "Not Rep", "")
c2015$TRAV_SP <- str_replace(c2015$TRAV_SP, "Unknown", "")
c2015$TRAV_SP <- as.numeric(c2015$TRAV_SP)
c2015 = c2015[!(is.na(c2015$TRAV_SP)),]
```

####3. Calculate the average age and average speed of female in the accident happened in the weekend.
##### Notice: These questions are to practice select_if and summarise_if, summarise_all. . . functions in dplyr
```{r}
c2015 %>%
  filter(SEX == "Female", DAY_WEEK %in% c("Friday", "Saturday", "Sunday")) %>% 
    summarize_at(vars(AGE, TRAV_SP), mean, na.rm=T)
```

#### 4. Use select_if and is.numeric functions to create a dataset with only numeric variables. Print out the names of all numeric variables
```{r}
c2015 %>% 
  select_if(is.numeric) %>% 
    names
```

#### 5. Calculate the mean of all numeric variables using select_if and summarise_all
```{r}
c2015 %>% 
  select_if(is.numeric) %>% 
    summarize_all(mean, na.rm = T)
```

#### 6. We can shortcut 3 and 4 by using summarise_if: Use summarise_if to Calculate the mean of all numeric variables. (You may need to use na.rm = TRUE to ignore the NAs)
```{r}
c2015 %>% 
  summarize_if(is.numeric, mean, na.rm=T)
```

#### 7. Use summarise_if to calculate the median of all numeric variables.
```{r}
c2015 %>% 
  summarize_if(is.numeric, median, na.rm=T)
```

#### 8. Use summarise_if to calculate the standard deviation of all numeric variables. (sd function for standard deviation)
```{r}
c2015 %>% 
  summarize_if(is.numeric, sd, na.rm=T)
```

#### 9. Use summarise_if to calculate the number of missing values for each numeric variables. Hint: Use ~sum(is.na(.))
```{r}
c2015 %>% 
  summarize_if(is.numeric, ~sum(is.na(.)))
```

#### 10. Calculate the log of the average for each numeric variable.
```{r}
c2015 %>% 
  summarize_if(is.numeric, mean, na.rm=T) %>% 
    log()
```

#### 11. You will notice that there is one NA is produced in 10. Fix this by calculating the log of the absolute value average for each numeric variable.
```{r}
c2015 %>% 
  summarize_if(is.numeric, mean, na.rm=T) %>% 
    abs() %>% 
      log()
```

#### 12. Calculate the number of missing values for each categorical variables using summarise_if
```{r}
c2015 %>% 
  summarize_if(is.character, ~sum(is.na(.)))
```

#### 13. Calculate the number of missing values for each categorical variables using summarise_all
```{r}
c2015 %>% 
  select_if(is.character) %>% 
    summarize_all(~sum(is.na(.)))
```

#### 14. Calculate the number of states in the dataset. **Hint: You can use length(table())
```{r}
c2015 %>%
  summarize_at(vars(STATE), ~length(table(.)))
```

#### 15. Calculate the number of uniques values for each categorical variables using summarise_if.
```{r}
c2015 %>% 
  summarize_if(is.character, ~length(table(.)))
```

#### 16. Calculate the number of uniques values for each categorical variables using summarise_all.
```{r}
c2015 %>% 
  select_if(is.character) %>% 
    summarize_all(~length(table(.)))
```

#### 17. Print out the names of all variables that have more than 30 distinct values
```{r}
c2015 %>% 
  summarize_all(~length(table(.))>30) %>% 
    names
```

#### 18. Print out the names of all categorical variables that more than 30 distinct values
```{r}
c2015 %>% 
  select_if(is.character) %>% 
    select_if(~length(table(.)) > 30) %>% 
      names
```

#### 19. Print out the names of all numeric variables that has the maximum values greater than 30
```{r}
c2015 %>% 
  select_if(is.numeric) %>%
    select_if(~max(.,na.rm=T) > 30) %>% 
      names
```

#### 20. Calculate the mean of all numeric variables that has the maximum values greater than 30 using ‘summarise_if’
```{r}
c2015 %>%
    select_if(~max(., na.rm=T) > 30) %>% 
      summarize_if(is.numeric, mean, na.rm = T)
```

#### 21. Calculate the mean of all numeric variables that has the maximum values greater than 30 using ‘summarise_all’
```{r}
 c2015 %>%
  select_if(is.numeric) %>% 
    select_if(~max(.,na.rm=T) > 30) %>% 
      summarize_all(~mean(.,na.rm=T))
```

#### 22. Create a dataset containing variables with standard deviation greater than 10. Call this data d1
```{r}
d1 <- c2015 %>% 
    select_if(is.numeric) %>% 
      select_if(~sd(.,na.rm=T) >10)
d1
```

#### 23. Centralizing a variable is subtract it by its mean. Centralize the variables of d1 using mutate_all. Check the means of all centralized variables to confirm that they are all zeros.
```{r}
d1 %>% 
  select_if(is.numeric) %>% 
    mutate_all(~(.) - mean(.,na.rm=T)) %>% 
      summarize_all(~mean(.,na.rm=T))
```

#### 24. Standarizing a variable is to subtract it to its mean and then divide by its standard deviation. Standardize the variables of d1 using mutate_all. Check the means and standard deviation of all centralized variables to confirm that they are all zeros (for the means) and ones (for standard deviation).
```{r}
#TRY TO DO IN ONE SUMMARIZE WITH A LIST
d1 %>% 
  select_if(is.numeric) %>% 
    mutate_all(~(. - mean(.,na.rm=T))/ sd(.,na.rm=T)) %>% 
      summarize_all(~mean(.,na.rm=T))

d1 %>% 
  select_if(is.numeric) %>% 
    mutate_all(~(. - mean(.,na.rm=T))/ sd(.,na.rm=T)) %>% 
      summarize_all(~sd(.,na.rm=T))
```


